---
output: 
pdf_document:
citation_package: natbib
keep_tex: false
fig_caption: true
latex_engine: pdflatex
title: 
author:
- name: Sangeeta Bhatia
affiliation: Imperial College London
abstract: 
keywords: 
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: 
biblio-style: apsr
endnote: no
---

## Same SI

```{r summary-1}
source("R/fig_utils.R")
si_mu_ref <- 5.4
si_std_ref <- 1.5
pretty_ci <- function(val, low, high, round_to = 2) {
  f <- function(x) {
    format(round(x, round_to), nsmall = 2)
  }
  glue("{f(val)} ({f(low)}, {f(high)})")
}

x <- readRDS("vary_si_err_summary_by_all_vars.rds")
x$label <- multiplier_label(x$si_mu_variant, 5.4)
x <- x[x$label %in% c("X 0.5", "X 1", "X 1.5", "X 2"), ]
same_si <- x[x$label == "X 1", ]
mu_qntls <- quantile(same_si$mu, c(0.025, 0.5, 0.975))
```
When the SI of both is same and is correctly specified, the 5 point
summary across all values of transmission advantage, reference Rt and SI mean
is 

```{r}
summary(same_si$mu)
```

### Same SI, uncertainty

```{r}
summary(same_si$sd)
```

## Different SI, correctly specified

```{r summary-2}
diff_si <- x[x$label != "X 1", ]

```
When the SI of both is different and is correctly specified, the mean error
across all values of transmission advantage, reference Rt and SI mean
is 

```{r}
summary(diff_si$mu)
```
Uncertainty:

```{r}
summary(diff_si$sd)
```

## Different CV, correctly specified

```{r summary-3}
x <- readRDS("vary_cv_err_summary_by_all_vars.rds")
x$label <- multiplier_label(x$si_cv_variant, si_std_ref / si_mu_ref)
x <- x[x$label %in% c("X 0.5", "X 1.5", "X 2"), ]
mu_qntls <- quantile(x$mu, c(0.025, 0.5, 0.975))
```
When the CV of the SI distribution of both is same and is correctly specified, the mean error
across all values of transmission advantage, reference Rt and SI mean
is `r pretty_ci(mu_qntls[2], mu_qntls[1], mu_qntls[3])`.


## Superspreading

```{r summary-4}
x <- readRDS("vary_offs_err_summary_by_all_vars.rds")
by_kappa <- split(x, x$kappa) %>%
  map_dfr(function(y) broom::tidy(summary(y$mu)), .id = "kappa")
```
### Bias by kappa

```{r}
knitr::kable(by_kappa)
```

### Overall bias

```{r}

summary(x$mu) %>%
  broom::tidy() %>%
  knitr::kable()

```
### Uncertainty by kappa


```{r}
knitr::kable(by_kappa)
```
### Overall Uncertainty 

```{r}

summary(x$sd) %>%
  broom::tidy() %>%
  knitr::kable()

```


```{r}
by_kappa <- split(x, x$kappa) %>%
  map_dfr(function(y) broom::tidy(summary(y$sd)), .id = "kappa")
```


## Underreporting

```{r summary-5}
x <- readRDS("underrep_err_summary_by_all_vars.rds")
by_preport <- split(x, x$p_report) %>%
  map_dfr(function(y) broom::tidy(summary(y$mu)), .id = "p_report")

```
With 20% reporting probability, the mean error
across all values of transmission advantage and reference Rts
is 

```{r}
knitr::kable(by_preport)
```

### Uncertainty 

```{r}
summary(x$sd) %>%
  broom::tidy() %>%
  knitr::kable()

```
## Classification stats

```{r summary-6}
infiles <- c(Underreporting = "underrep_classified.rds",
             `Different SI CV` = "vary_cv_classified.rds",
             Superspreading = "vary_offs_classified.rds", 
             `Different SI Mean` = "vary_si_classified.rds",
             `Misspecified CV` = "wrong_cv_classified.rds",
             `Misspecified Mean` = "wrong_si_classified.rds")

classified <- map(infiles, readRDS)

classified <- map(
  classified, function(x) {
    x <- mutate_if(x, is.numeric, percent, 0.1)
    spread(x, classification, val)
  })
x50 <- map_dfr(classified, ~ .[.$tmax == 50, ], .id = "scenario")
```

```{r summary-7}
knitr::kable(x50[, c(-2, -3)])
```

## Summary of SARS-CoV-2 Variants

```{r}
x <- readRDS("epsilon_qntls_over_time.rds")
y <- readRDS("epsilon_qntls_per_region.rds")
z <- readRDS("epsilon_qntls_whole_country.rds")
```

We estimated the effective transmission advantage of 
- Alpha over wildtype in England to be 
`r pretty_ci(z$uk_alpha_wild[[3]], z$uk_alpha_wild[[2]], z$uk_alpha_wild[[4]])`
- Alpha over wildtype in France to be 
`r pretty_ci(z$french[[3]], z$french[[2]], z$french[[4]])`


### Regional differences in estimates using MV-EpiEstim

#### UK - Alpha over Wild

```{r}
y$uk_alpha_wild <- arrange(y$uk_alpha_wild, y$uk_alpha_wild[["50%"]])
regional_cis <- pretty_ci(y$uk_alpha_wild[[4]], y$uk_alpha_wild[[3]], y$uk_alpha_wild[[5]])
```


```{r}
knitr::kable(data.frame(region = y$uk_alpha_wild$region, CI = regional_cis))
```

### Temporal differences in estimates using MV-EpiEstim

The central estimate of the effective transmission advantage for Alpha
increased from 
- `r pretty_ci(x$uk_alpha_wild[[4]][1], x$uk_alpha_wild[[3]][1], x$uk_alpha_wild[[5]][1])` to
- `r pretty_ci(x$uk_alpha_wild[[4]][26], x$uk_alpha_wild[[3]][26], x$uk_alpha_wild[[5]][26])`
