---
output: 
pdf_document:
citation_package: natbib
keep_tex: false
fig_caption: true
latex_engine: pdflatex
title: 
author:
- name: Sangeeta Bhatia
affiliation: Imperial College London
abstract: 
keywords: 
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: 
biblio-style: apsr
endnote: no
---

## Same SI

```{r summary-1}
source("R/fig_utils.R")
si_mu_ref <- 5.4
si_std_ref <- 1.5
pretty_ci <- function(val, low, high, round_to = 2) {
  f <- function(x) {
    format(round(x, round_to), nsmall = 2)
  }
  glue("{f(val)} ({f(low)}, {f(high)})")
}

x <- readRDS("vary_si_err_summary_by_all_vars.rds")
x$label <- multiplier_label(x$si_mu_variant, 5.4)
x <- x[x$label %in% c("X 0.5", "X 1", "X 1.5", "X 2"), ]
same_si <- x[x$label == "X 1", ]
mu_qntls <- quantile(same_si$mu, c(0.025, 0.5, 0.975))
```
When the SI of both is same and is correctly specified, the mean error
across all values of transmission advantage, reference Rt and SI mean
is `r pretty_ci(mu_qntls[2], mu_qntls[1], mu_qntls[3])`.

## Different SI, correctly specified

```{r summary-2}
diff_si <- x[x$label != "X 1", ]
mu_qntls <- quantile(diff_si$mu, c(0.025, 0.5, 0.975))
```
When the SI of both is different and is correctly specified, the mean error
across all values of transmission advantage, reference Rt and SI mean
is `r pretty_ci(mu_qntls[2], mu_qntls[1], mu_qntls[3])`.

## Different CV, correctly specified

```{r summary-3}
x <- readRDS("vary_cv_err_summary_by_all_vars.rds")
x$label <- multiplier_label(x$si_cv_variant, si_std_ref / si_mu_ref)
x <- x[x$label %in% c("X 0.5", "X 1.5", "X 2"), ]
mu_qntls <- quantile(x$mu, c(0.025, 0.5, 0.975))
```
When the CV of the SI distribution of both is same and is correctly specified, the mean error
across all values of transmission advantage, reference Rt and SI mean
is `r pretty_ci(mu_qntls[2], mu_qntls[1], mu_qntls[3])`.


## Superspreading

```{r summary-4}
x <- readRDS("vary_offs_err_summary_by_all_vars.rds")
mu_qntls <- group_by(x, kappa) %>%
  summarise(
    low = quantile(mu, 0.025),
    med = quantile(mu, 0.5),
    high = quantile(mu, 0.975)
  ) %>% ungroup()
            

```
For SARS like spread, the mean error
across all values of transmission advantage and reference Rts
is `r pretty_ci(mu_qntls[[2]][1], mu_qntls[[3]][1], mu_qntls[[4]][1])`.

For Ebola like spread, the mean error
across all values of transmission advantage and reference Rts
is `r pretty_ci(mu_qntls[[2]][2], mu_qntls[[3]][2], mu_qntls[[4]][2])`.

## Underreporting

```{r summary-5}
x <- readRDS("underrep_err_summary_by_all_vars.rds")
mu_qntls <- group_by(x, p_report) %>%
  summarise(
    low = quantile(mu, 0.025),
    med = quantile(mu, 0.5),
    high = quantile(mu, 0.975)
  ) %>% ungroup()            
```
With 20% reporting probability, the mean error
across all values of transmission advantage and reference Rts
is `r pretty_ci(mu_qntls[[2]][1], mu_qntls[[3]][1], mu_qntls[[4]][1])`.

With 50% reporting probability, the mean error
across all values of transmission advantage and reference Rts
is `r pretty_ci(mu_qntls[[2]][2], mu_qntls[[3]][2], mu_qntls[[4]][2])`.

## Classification stats

```{r summary-6}
infiles <- c(Underreporting = "underrep_classified.rds",
             `Different SI CV` = "vary_cv_classified.rds",
             Superspreading = "vary_offs_classified.rds", 
             `Different SI Mean` = "vary_si_classified.rds",
             `Misspecified CV` = "wrong_cv_classified.rds",
             `Misspecified Mean` = "wrong_si_classified.rds")

classified <- map(infiles, readRDS)

classified <- map(
  classified, function(x) {
    x <- mutate_if(x, is.numeric, percent, 0.1)
    spread(x, classification, val)
  })
x50 <- map_dfr(classified, ~ .[.$tmax == 50, ], .id = "scenario")
```

```{r summary-7}
knitr::kable(x50[, c(-2, -3)])
```


